Supplementary Information: Improving Monocular Depth Estimation with Global Depth Histogram Matching

### 2019-10-09 paper/cvpr2020/main.tex
Added pseudocode for exact histogram matching.
full pass over experimental results section

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{multirow}
\usepackage{float}
\usepackage[utf8x]{inputenc}
\input{mark_defs.tex}

@@

\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

>>>>

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{multirow}
\usepackage{float}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}

\usepackage{dblfloatfix}

\input{mark_defs.tex}

@@

\graphicspath{{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

### 2019-10-09 paper/cvpr2020/sections/hardware.tex
full pass over experimental results section

\textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}

Missing:
%
\begin{itemize}
\item RGB resolution used for MDE
\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
\end{itemize}

@@

>>>>

%We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
%the scanning system using the standard camera calibration toolbox in MATLAB.
%In general it is impossible to compensate for the offset between camera and
%SPAD, but we do add the z displacement from spad to kinect to partially
%compensate for it.
%% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
%
%Missing:
%%
%\begin{itemize}
%\item RGB resolution used for MDE
%\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
%\end{itemize}

@@

Using this prototype, we captured a number of scenes as shown in Figure~\ref{fig:results_captured} and in the supplement. We downsample the reference RGB image to a resolution of $XX \times XX$~px and directly feed into a monocular depth estimation algorithm. In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested. Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement. The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).

In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonable well. However, the root mean squared error (RMSE) for these two scenes is relatively high with 2.4--2.9~m (see red/white error maps in Fig.~\ref{fig:results_captured}). The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m. The ``Poster'' scene is meant to confuse the CNN---it shows a flat poster with a printed scene. As expected, the CNN predicts that the statue is closer than the arches in the background, which is incorrect in this case. The proposed method uses the SPAD histogram to correctly flatten the estimated depth map.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured_results_main}
	\caption{Experimental results. For each scene, we record an RGB image (lower left subimages) and a ground truth depth map that is raster-scanned with the SPAD (upper left subimages). A monocular depth CNN often predicts the ordinal depth well (top two scenes), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages) as shown by the error maps and root mean squared error (RMSE) for each example (lower center and right subimages). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

### 2019-10-09 paper/cvpr2020/supplement.tex
full pass over experimental results section

>>>>

\graphicspath{{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
